---
title: "Fakebook Bus Seat Selection Analysis"
author: "Meriem Mehri"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
header-includes:
   - \usepackage{graphbox} # for including images right aligned
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align='center', fig.show='hold')
library(tidygraph)
library(ggraph)
library(dplyr)
library(ggplot2)
```

# Introduction

This document provides an analysis of the seating arrangement on the Fakebook company bus. As a new intern, selecting the right seat is critical for fostering connections within the company. The seats are analyzed based on their centrality measures within the network.

# Network Centrality Measures

First, we calculate the centrality measures for each seat to understand their importance within the network.

```{r centrality-measures, echo=TRUE}
# Define the edges of the seating arrangement
edges <- tribble(
  ~from, ~to,
  "1", "2", "1", "A", "1", "B",
  "2", "1", "2", "3", "2", "A",
  "3", "2", "3", "4", "3", "B", "3", "C",
  "4", "3", "4", "5", "4", "C",
  "5", "4", "5", "6", "5", "D",
  "6", "5", "6", "B", "6", "D",
  "A", "1", "A", "2", "A", "B",
  "B", "A", "B", "1", "B", "3", "B", "6", "B", "D",
  "C", "3", "C", "4", "C", "D",
  "D", "C", "D", "5", "D", "6", "D", "B"
) %>%
  as_tbl_graph(directed = FALSE) %>%
  activate(nodes) %>%
  mutate(name = as.character(name))

# Calculate centrality measures for the network
centrality_measures <- edges %>%
  mutate(degree = centrality_degree(),
         closeness = centrality_closeness(),
         betweenness = centrality_betweenness(),
         color = case_when(
           name %in% c("A", "B", "C", "D") ~ 'red',
           TRUE ~ 'blue'
         ))

# Print centrality measures for chosen seats
chosen_seats <- centrality_measures %>%
  filter(name %in% c("A", "B", "C", "D")) %>%
  arrange(name)
```

## Seating Arrangement Network Plot

Next, we visualize the network plot with the calculated centrality measures.

```{r network-plot, fig.cap="Network plot showing the centrality measures for the seating arrangement on the Fakebook bus.", fig.width=7, fig.height=7, echo=FALSE}
# Plot the network
network_plot <- ggraph(centrality_measures, layout = 'stress') +
  geom_edge_link(edge_width = 1, color = 'gray') +
  geom_node_point(aes(color = color), size = 8) +
  geom_node_text(aes(label = name), repel = TRUE, fontface = "bold", color = "black") +
  theme_graph() +
  labs(title = "Bus Seating Arrangement and Centrality Measures",
       subtitle = "Highlighting Seats A, B, C, D") +
  scale_color_manual(values = c('red', 'blue'), labels = c("Chosen Seats", "Other Seats")) +
  guides(color = guide_legend(title = "Seat Type")) +
  theme(legend.position = "bottom", legend.title = element_text(size = 10), legend.text = element_text(size = 8))

network_plot
```

# Interpretation of Centrality Measures

The network plot highlights Seats A, B, C, and D as potential choices for the new intern at Fakebook, shown in red. These seats are analyzed based on their centrality within the bus social network.

- **Seat A**: High betweenness but lower degree centrality. Ideal for an intern looking to bridge different social clusters, potentially influencing the network's communication flow.

- **Seat B**: Offers the highest degree centrality, suggesting it is